---
title: "master_thesis"
author: "LInda Kladivova"
date: "22 4 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Introduction to data and setting up

```{r Setting up}
library("reshape2")
library("pacman") #this package allows us to use the `pload()` function below to load multiple packages in one line
p_load(rgdal, sf, tidyverse, tmap, spData, spatstat, maptools, ggrepel, ggspatial, rworldmap, rworldxtra)

```


```{r question1}

# Read in data
question1 <- read.csv(file = "C:/Users/kladivoval/dp-kladivova-2021/surveys/raw_data/survey1_part1_question1.csv", stringsAsFactors = FALSE, sep = ';')
dim(question1)
head(question1)
tail(question1)
```

```{r question3}

# Read in data
question3 <- read.csv(file = "C:/Users/kladivoval/dp-kladivova-2021/surveys/raw_data/survey1_part1_question3.csv", stringsAsFactors = FALSE, sep = ';')
dim(question3)
head(question3)
tail(question3)

```

```{r question5}

# Read in data
question5 <- read.csv(file = "C:/Users/kladivoval/dp-kladivova-2021/surveys/raw_data/survey1_part1_question5.csv", stringsAsFactors = FALSE, sep = ';')
dim(question5)
head(question5)
tail(question5)

```

```{r question6}

# Read in data
question6 <- read.csv(file = "C:/Users/kladivoval/dp-kladivova-2021/surveys/raw_data/survey1_part1_question6.csv", stringsAsFactors = FALSE, sep = ';')
dim(question6)
head(question6)
tail(question6)

```

```{r survey1_part2_question5}

# Read in data
question5_2 <- read.csv(file = "C:/Users/kladivoval/dp-kladivova-2021/surveys/raw_data/survey1_part2_question5.csv", stringsAsFactors = FALSE, sep = ';')
dim(question5_2)
head(question5_2)
tail(question5_2)

```


### EDA: Overall descriptive statistics and histograms

```{r descriptive statistics }

# Convert sp object to dataframe
summary(question1)
summary(question3)
summary(question5)
summary(question6)
summary(question5_2)

question5_sub = question5%>% select(Responses)
ggplot(data=reshape2::melt(question5_sub)) +
  geom_histogram(mapping=aes(x=value, fill=variable)) +
  facet_wrap(~variable, scales = ("free"), nrow=1) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 30))

```

### EDA: Boxplots for ranking questions

Furthermore, we can identify where the bulk of our data sits and identify the presence of outliers.
Similarly as with histograms, We can also create more boxplots within one plot using DPLYR.

```{r package data box2, out.width ='\\maxwidth'}

# QUESTION 3
question3_sub = question3 %>% select(Mapset_access_info, Deleting_multiple_mapsets_or_locations, Adding_multiple_databases, Creating_renaming_deleting_mapset_or_location, New_management_icons, Small_icons_distinquishing_mapsets.., Removing_deleting_GRASS_database)
ggplot(data=reshape2::melt(question3_sub)) +
  geom_boxplot(mapping=aes(x=value, y=value, fill=variable)) +
  guides(fill = guide_legend(title = "New features in GRASS GIS"))+
  ylab("Ranking (1 = most useful)") + xlab("") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 7))
  
```

```{r package data box3, out.width ='\\maxwidth'}

# QUESTION 5
question5_2_sub = question5_2%>% select(Description_of_main_tabs, Description_of_what_database_location_mapset_means, Brief_advice_on_how_to_start)
ggplot(data=reshape2::melt(question5_2_sub)) +
  geom_boxplot(mapping=aes(x=value, y=value, fill=variable)) +
  guides(fill = guide_legend(title = "Suggested features helping in initial orientation in the software"))+
  ylab("Ranking (1 = most important)") + xlab("") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3))

ggplot(data=reshape2::melt(question5_2_sub)) +
  geom_histogram(mapping=aes(x=value, fill=variable), bins=50) +
  guides(fill = guide_legend(title = "Features enhancing first-time user experience in GRASS GIS"))+
  xlab("Ranking (1 = most important)") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 20))

```


### EDA: Probability and cumulative density functions

We can go a little further and check probability density functions (geom_density) and empirical cumulative distribution functions using ggplot. 


```{r package data pdf1, out.width ='\\maxwidth'}

# QUESTION 1
question1_sub = question1%>% select(Responses)
ggplot(data=reshape2::melt(question1_sub)) +
  geom_density(mapping=aes(x=value, fill=variable), na.rm=T, alpha=0.5) +
  xlab("Degree of agreement with the statement")
```

```{r package data pdf2, out.width ='\\maxwidth'}

# QUESTION 3
question3_sub = question3 %>% select(Mapset_access_info, Deleting_multiple_mapsets_or_locations, Adding_multiple_databases, Creating_renaming_deleting_mapset_or_location, New_management_icons, Small_icons_distinquishing_mapsets.., Removing_deleting_GRASS_database)
ggplot(data=reshape2::melt(question3_sub)) +
  geom_density(mapping=aes(x=value, fill=variable), na.rm=T, alpha=0.5) +
  guides(fill = guide_legend(title = "New features in GRASS GIS"))+
  xlab("Ranking (1 = most useful)")

```

```{r package data pdf3, out.width ='\\maxwidth'}

# QUESTION 6
question6_sub = question6%>% select(Responses)
ggplot(data=reshape2::melt(question6_sub)) +
  geom_density(mapping=aes(x=value, fill=variable), na.rm=T, alpha=0.5) +
  xlab("Degree of agreement with the statement")

```

```{r package data pdf4, out.width ='\\maxwidth'}
# QUESTION 5.2
question5_2_sub = question5_2%>% select(Description_of_main_tabs, Description_of_what_database_location_mapset_means, Brief_advice_on_how_to_start)
ggplot(data=reshape2::melt(question5_2_sub)) +
  geom_density(mapping=aes(x=value, fill=variable), na.rm=T, alpha=0.5) +
  guides(fill = guide_legend(title = "Suggested features helping in initial orientation in the software"))+
  xlab("Ranking (1 = most important)")

```
